Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-29 paper_jasa.tex
modeling effect size

@@

>>>>

The main covariate factors that determine the power of the test are sample size ($n$), $\sigma$ and the parameter $\beta$. combining these we obtain one single covariate effect denoted by $E$ and defined as $E = \beta/ \sigma*\sqrt{n}$. Using equation \ref{mixed}, we then have the power as

\begin{equation}\label{eqn:effect} 
Power(E) = \pi=Pr(Y=1| E) 
\end{equation}

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.7}{\includegraphics{effect_power_exp1.pdf}}
       \caption{Observed power shown by loess smoother and the power of UMP test for different effect size $E$ as per experiment 1.}
       \label{fig:power_loess1}
\end{figure*}
